### 2013-07-06 cws/emnlp_cws/conclusion.tex
grammatical edits mostly

In this paper we presented an approach to Chinese word segmentation using dual decomposition for system combination. We demonstrated that this method allows for joint decoding of existing CWS systems that are more accurate and consistent than either system alone, and further achieves the best performance reported to date on standard datasets for the task.
Perhaps most importantly, our approach is straightforward to implement and does not require retraining of the underlying segmentation models used. This suggests its potential for broader applicability in real-world settings than existing approaches to combining character-based and word-based models for Chinese word segmentation.

>>>>

In this paper we presented an approach to Chinese word segmentation using dual decomposition for system combination. We demonstrated that this method allows for joint decoding of existing CWS systems that is more accurate and consistent than either system alone, and further achieves the best performance reported to date on standard datasets for the task.
Perhaps most importantly, our approach is straightforward to implement and does not require retraining of the underlying segmentation models used. This suggests its potential for broader applicability in real-world settings than existing approaches to combining character-based and word-based models for Chinese word segmentation.

### 2013-07-06 cws/emnlp_cws/discussion.tex
grammatical edits mostly

A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or product-of-experts model could not, since joint decoding allows the sharing of information at decoding time. In the following example, both baseline models miss the contextually clear grammatical role of 上 (``above") and instead produce the otherwise common compound 上去 (``go up"); dual decomposition allows the model to generate the correct segmentation.
\begin{small}
\begin{tabbing}
\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy / a bit of / snack food / , ... \\
\> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\
\> \emph{CRF} \> 享受 / 一点点 / 心 / ，\\
\> \emph{PCPT} \> 享受 / 一点点 / 心 / ， \\
\> \emph{DD} \>  享受 / 一点 / 点心 / ，\\
\end{tabbing}
\end{small}
We found more than 400 such surprisingly accurate instances in our dual decomposition output.

>>>>

A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or product-of-experts model could not, since joint decoding allows the sharing of information at decoding time. In the following example, both baseline models miss the contextually clear use of the word 点心 (``sweets / snack food") and instead attach 点 to the prior word to produce the otherwise common compound 一点点 (``a little bit"); dual decomposition allows the model to generate the correct segmentation.
\begin{small}
\begin{tabbing}
\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy / a bit of / snack food / , ... \\
\> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\
\> \emph{CRF} \> 享受 / 一点点 / 心 / ，\\
\> \emph{PCPT} \> 享受 / 一点点 / 心 / ， \\
\> \emph{DD} \>  享受 / 一点 / 点心 / ，\\
\end{tabbing}
\end{small}
We found more than 400 such surprisingly accurate instances in our dual decomposition output.

### 2013-07-06 cws/emnlp_cws/experiment.tex
grammatical edits mostly

We conduct experiments  on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual decomposition algorithm. We take the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development. The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration ($T$ in Algo.~\ref{algo:DD}) of 100 with step size ($\alpha_t$ in Algo.~\ref{algo:DD}) 0.1. Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}. They have shown that increased segmentation consistency is correlated with better machine translation performance. The consistency measure calculates the entropy of segmentation variations --- the lower the score the better. Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

>>>>

We conduct experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets to evaluate the effectiveness of the proposed dual decomposition algorithm. We use the publicly available Stanford CRF segmenter \cite{Tseng:2005:SIGHAN}\footnote{http://nlp.stanford.edu/software/segmenter.shtml} as our character-based baseline model, and reproduce the perceptron-based segmenter from \newcite{Zhang:2007:ACL} as our word-based baseline model.
We adopted the development setting from \cite{Zhang:2007:ACL}, and used CTB sections 1-270 for training, and sections 400-931for development. The optimized hyper-parameters used are: $\ell_{2}$ regularization parameter $\lambda$ in CRF is set to $3$; perceptron is trained for 10 iterations with beam size 200; dual decomposition is run to max iteration ($T$ in Algo.~\ref{algo:DD}) of 100 with step size ($\alpha_t$ in Algo.~\ref{algo:DD}) 0.1. Other than the standard precision (P), recall (R) and F$_1$ scores, we also evaluate segmentation consistency as proposed by \cite{Chang:2008:ACL}, who have shown that increased segmentation consistency is correlated with better machine translation performance. The consistency measure calculates the entropy of segmentation variations --- the lower the score the better. Statistical significance tests are done using the paired bootstrap resampling method \cite{efron93bootstrap}.

### 2013-07-06 cws/emnlp_cws/models.tex
grammatical edits mostly

\subsection{Character-based Models}
In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word. Conditional random field (CRF) \cite{Lafferty:2001:ICML} is widely adopted for this task, and gives state-of-the-art results \cite{Tseng:2005:SIGHAN}. In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
\begin{align*}\vspace{-10em}
P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp\left( \theta \cdot {f}(x, y_t, y_{t+1}) \right) }}
\vspace{-10em}
\end{align*}
\noindent $f(x, y_{t}, y_{t-1})$ are features functions that typically include surrounding n-gram and morphological suffix/prefix features. These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.  
But the Markov assumption in CRF limits the context of such features; it is difficult to capture long-range word features in this model. 
%, which is important for admitting efficient inference, restricts the CRF to very local context features. A first-order CRF can only reason about character boundary decisions of current and neighboring positions. 
%It is therefore difficult to directly model words of greater length. Although higher-order CRF could potentially alleviate this problem, and has been applied to CWS \cite{Zhao:2007:ICNC}, it comes at the cost of exponentially higher model complexity.

\subsection{Word-based Models}
Word-based models searches through lists of word candidates using scoring functions that directly assign scores to word candidates. 
Early word-based segmentation work employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}. 
 \newcite{Zhang:2007:ACL} reported more recent success using a linear model trained with the average perceptron algorithm \cite{Collins:2002:EMNLP}.
 Formally, given input $\mathbf{x}$, their models seeks for a segmentation $F(\mathbf{x})$ such that:
\begin{align*}
F(\mathbf{y}|\mathbf{x}) =  \argmax{ \left( \alpha \cdot \phi(\mathbf{\mathbf{y}}) \right) }
\end{align*}
\noindent Searching through the entire $\mathrm{GEN}(\mathbf{x})$ space is intractable even with a local model. A beam-search algorithm is therefore employed. The search algorithm consumes one character input token at a time, and iterate through the existing beams to score two new alternative hypotheses by either appending the new character to the last word in the beam, or start a new word at current position.

@@

\subsection{Combine Models with Dual Decomposition} 
Various mixing approaches have been proposed to combine the above two approaches \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}. 
These mixing models perform well on standard datasets, but are not in wide use because of their high computational costs and difficulty of implementation.

Dual decomposition (DD) \cite{Rush:2010:EMNLP} offers an attractive framework for combining these two types of models without incurring high cost in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}). DD has been successfully applied to similar situations where we want to combine local model with global models, for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.

The idea is that jointly model both character-sequence and word information can be computationally challenging,  instead we could try to find outputs that the two models are most likely to agree on.
Formally, the objective of DD is:
\begin{align*}
   \max_{\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}}  \; P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) \;  \ni \mathbf{y^\textit{c}} = \mathbf{y^\textit{w}}
\end{align*}
\noindent where $\mathbf{y^\textit{c}}$ is the output of character-based CRF and $\mathbf{y^\textit{w}}$ is the output of word-based perceptron.

The DD algorithm is an iterative procedure: in each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other. This penalty exchange is similar to message passing, and as the penalty accumulate over the iterations, the two models are pushed towards agreeing with each other. We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algo.~\ref{algo:DD}\footnote{Due to space limitation, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.

>>>>

\subsection{Character-based Models}
In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word. Conditional random fields (CRF) \cite{Lafferty:2001:ICML} are widely adopted for this task, and give state-of-the-art results \cite{Tseng:2005:SIGHAN}. In a first-order linear-chain CRF model, the conditional probability of a label sequence $\mathbf{y}$ given a word sequence $\mathbf{x}$ is defined as:
\begin{align*}\vspace{-10em}
P(\mathbf{y} | \mathbf{x}) = \frac{1}{Z}{ \sum\limits_{t=1}^{|\mathbf{y}|}{ \exp\left( \theta \cdot {f}(x, y_t, y_{t+1}) \right) }}
\vspace{-10em}
\end{align*}
\noindent $f(x, y_{t}, y_{t-1})$ are feature functions that typically include surrounding n-gram and morphological suffix/prefix features. These types of features capture the compositional properties of characters and are likely to generalize well to unknown words.  
However, the Markov assumption in CRF limits the context of such features; it is difficult to capture long-range word features in this model. 
%, which is important for admitting efficient inference, restricts the CRF to very local context features. A first-order CRF can only reason about character boundary decisions of current and neighboring positions. 
%It is therefore difficult to directly model words of greater length. Although higher-order CRF could potentially alleviate this problem, and has been applied to CWS \cite{Zhao:2007:ICNC}, it comes at the cost of exponentially higher model complexity.

\subsection{Word-based Models}
Word-based models search through lists of word candidates using scoring functions that directly assign scores to each. 
Early word-based segmentation work employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}. 
More recently, \newcite{Zhang:2007:ACL} reported success using a linear model trained with the average perceptron algorithm \cite{Collins:2002:EMNLP}.
 Formally, given input $\mathbf{x}$, their model seeks a segmentation $F(\mathbf{x})$ such that:
\begin{align*}
F(\mathbf{y}|\mathbf{x}) =  \argmax{ \left( \alpha \cdot \phi(\mathbf{\mathbf{y}}) \right) }
\end{align*}
\noindent Searching through the entire $\mathrm{GEN}(\mathbf{x})$ space is intractable even with a local model, so a beam-search algorithm is used. The search algorithm consumes one character input token at a time, and iterates through the existing beams to score two new alternative hypotheses by either appending the new character to the last word in the beam, or starting a new word at the current position.

@@

\subsection{Combining Models with Dual Decomposition} 
Various mixing approaches have been proposed to combine the above two approaches \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}. 
These mixing models perform well on standard datasets, but are not in wide use because of their high computational costs and difficulty of implementation.

Dual decomposition (DD) \cite{Rush:2010:EMNLP} offers an attractive framework for combining these two types of models without incurring high costs in model complexity (in contrast to \cite{Sun:2009:HLT-NAACL}) or decoding efficiency (in contrast to bagging in \cite{Wang:2006:SIGHAN,Sun:2010:COLING}). DD has been successfully applied to similar situations for combining local with global models; for example, in dependency parsing \cite{Koo:2010:EMNLP}), bilingual sequence tagging \cite{Wang:2013:ACL} and word alignment \cite{Denero:2011:ACL}.

The idea is that jointly modelling both character-sequence and word information can be computationally challenging, so instead we can try to find outputs that the two models are most likely to agree on.
Formally, the objective of DD is:
\begin{align*}
   \max_{\mathbf{y^\textit{c}}, \mathbf{y^\textit{w}}}  \; P(\mathbf{y^\textit{c}} | \mathbf{x}) + F(\mathbf{y^\textit{w}} | \mathbf{x}) \;  \ni \mathbf{y^\textit{c}} = \mathbf{y^\textit{w}}
\end{align*}
\noindent where $\mathbf{y^\textit{c}}$ is the output of character-based CRF and $\mathbf{y^\textit{w}}$ is the output of word-based perceptron.

The DD algorithm is an iterative procedure: in each iteration, if the best segmentations provided by the two models do not agree, then the two models will receive penalties for the decisions they made that differ from the other. This penalty exchange is similar to message passing, and as the penalty accumulates over iterations, the two models are pushed towards agreeing with each other. We give an updated Viterbi decoding algorithm for CRF and a modified beam-search algorithm for perceptron, as well as pseudo-code for DD algorithm in Algo.~\ref{algo:DD}\footnote{Due to space limitations, we defer to the tutorial of \newcite{Rush:2012:JAIR} for a full introduction of DD.}.
